An HPSG account for verbal reduplication in Mandarin Chinese

### 2024-07-13 replies-reviews.tex

\begin{enumerate}
\item This paper presents an innovative analysis of verb reduplication in Mandarin Chinese, demonstrating
clarity and well-organized sections. To enhance clarity, I recommend providing a brief illustration for
technical terms like LTOP, catering to readers less familiar with them.
The authors employ various tests to assert that verb reduplication exhibits more word-like
characteristics than phrase-like, hence justifying its morphological classification. The subsequent
adoption of a Head-Driven Phrase Structure Grammar (HPSG) framework, integrating Minimal
Recursion Semantics (Copestake et al., 2005), presents advantages over prior analyses.
Despite these strengths, certain questions warrant attention. The primary concern revolves around
treating verb reduplication as morphological. The authors compare it with Parallel Verb Compound
(PVC) and Serial Verb Construction (SVC), asserting that verb reduplication aligns more closely with
SVC than PVC in tests like phrase extension, substitution, and conjunction reduction. However, the
choice of SVC over regular verb phrases as a point of comparison with PVC and verb reduplication
lacks clarity. While SVC passes these tests, it is crucial to note that regular verb phrases may not pass
some, e.g., separate modification of subparts within a constituent.
In light of this, concluding that verb reduplication is more word-like and less phrase-like is
questionable, as regular verb phrases encounter similar challenges. Therefore, it is crucial to
explicitly justify why SVC was chosen over regular verb phrases for this comparison. Providing such
clarification will strengthen the robustness of the paper's argumentation and render the conclusion
that verb reduplication should be morphological more convincing.
For additional comments, please refer to the attached PDF file.

@@

%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%
%% YL
R2 comments on the following passage: The current study will only focus on the AA, A-yi-A, A-le-A, A-le-yi-A, ABAB and
AB-le-AB forms of verbal reduplication in Mandarin Chinese. AA-kan, A-kan-kan,
AAB, A-yi-AB, A-le-AB will also be mentioned.

One of the key questions addressed in this paper pertains to whether verb reduplication is best understood as a morphological or a syntactic phenomenon. However, it's noteworthy that the forms emphasized in this paper are all instances of syntactic verb reduplication (Xie, 2020).

To further enrich the ongoing debate, I wonder whether the authors will consider the inclusion of examples that previous studies have identified as morphological verb reduplications. This addition would help demonstrate the broader scope and applicability of your analysis. Alternatively, it would be beneficial to clarify the reasons for selecting these specific forms in this article.

%%%%%%%%%%%%%%%%
\textbf{Answer:} 
\citet{Xie2020} identifies the AABB form as morphological verb reduplication.
Even though we do not agree with \citegen{Xie2020} claim that the distinction between ABAB and AABB lies in the distinction between morphology and syntax,
we do agree that they are different grammatical processes and thus requires separate analyses (See also \citealt[Sec. 4.3]{Deng2013}, \citealt{Wang2023}).
Also note that there are numerous scholars that do consider the forms analyzed here as morphological processes (\citealt[Ch. 4]{Chao1968}, \citealt[Ch. 3]{LiThompson1981}, \citealt[4--5]{Liao2014} and \citealt[Sec. 4]{Sui2018}).
\citet[14--15]{Zhang2000} argues that the AABB form of reduplication develops from a completely separate historical origin from the AA and ABAB forms, 
as the former has a intensifying rather than delimitative meaning.
\citet[83--84]{Xie2020} further points out that AABB is much less productive than ABAB.
This suggests that at least some AABB might not be formulated by rules but is stored in the lexicon as a whole.
This is probably the case for those AABBs that have an idiomatic meaning, such as \textit{zhi-zhi-dian-dian} `point-point-gesture-gesture, gossip'.
%Productively formed AABBs can be accounted for by the current analysis as the reduplication happens before the compounding process,
%i.e. monosyllabic verbs are reduplicated separately (as AA and BB respectively) and then compounded together to form AABB.
%This is in line with the proposal in \citet[Sec. 4.2]{Wang2023},
%and also explains why some AABBs do not have a base AB form, such as \textit{zou-zou-ting-ting} `walk-walk-stop-stop, walk for a while and rest for a while', *\textit{zou-ting} `walk-stop'
The current analysis has a broad scope in that it explains all forms of delimitative verbal reduplication, which previous analyses were not able to do.
An analysis for the AABB form of reduplication has to be left for further research.

%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%
%% YL
\item 
R2 comments on the following passage: The meaning of the reduplication is not compositional, as it does
not mean that the event denoted by the verb happens twice or multiple times, but
rather that the event happens for a short duration and/or for low frequency. This
non-compositionality suggests that a reduplication is more word-like.

@@

(2) * ta dakai qingsheng de men. 
         he open quietly       DE door
         'He opened the door quietly.'

The key consideration here is that the unacceptability of (26b) and examples such as (2) may not hinge solely on whether part of it can be modified. Instead, it could be associated with the post-verbal placement of the adverb.

Consequently, it becomes challenging to use these examples as support for the argument that verb reduplication should be classified as a morphological rather than a syntactic phenomenon. This is because even regular verb phrases cannot be partially modified in the same manner.

\textbf{Answer:} %Yes, this is true.

\item Examples (27) and (28) serve as illustrations to demonstrate the application of the 'Lexical Integrity Hypothesis' in distinguishing PVC from SVC.

@@

In reference to (25), it is explained that the Lexical Integrity Hypothesis posits that 'No
phrase-level rule may affect a proper subpart of a word.' However, it is noteworthy that the authors
employ le-insertion in (27) and (28), indicating that le- cannot be inserted into PVC but can be
inserted into SVC. This might suggest that the use of le-insertion in these examples could be
construed as a form of phrase-level operation, potentially conflicting with the author's perspective
of regarding 'le' as a morphological process.

Regarding example (34), the conjunctive structures do not exhibit conjunction reduction, a phenomenon that typically requires a degree of overlap between two elements, as shown in (32). Example (34) presents a scenario where there is no overlap between the verb structures.

Moreover, in Mandarin, conjunctions can only be employed with nouns and not with verbs phrases or
clauses (Schafer, 2009). If this holds true, it is less likely to observe conjunction reduction for
verb phrases. Consequently, it would be inappropriate to assert that verb reduplication is more
word-like and less phrase-like, as even regular verb phrases may encounter problems undergoing
conjunction reduction.

\item In Section 2.4, the authors asserted that verb reduplication is more phrase-like than word-like based on its similarities with Parallel Verb Compounds as apposed to Serial Verb Construction (SVC).

@@

However, it is crucial to acknowledge that SVC has distinctive features, some of which diverge from those of a standard verb phrase. This raises a concern that a verb phrase might not successfully pass certain tests applicable to SVC, such as the ability for a constituent to be partially modified (A regular verb phrase like 'Verb + Object' cannot be partially modified by an adverb, while each verb in an SVC structure can be modified separately (28)). Therefore, when verb reduplication cannot be partially modified, asserting that it is less phrase-like solely on the basis of its differences from SVC might be inappropriate. This is because even a regular verb phrase faces limitations.

In light of this, it becomes essential to clarify why SVC, rather than regular verb phrases, was
chosen as a comparison to Parallel Verb Compounds. Such clarification would enhance the
persuasiveness of the tests presented in this section.

%%%%%%%%%%%%%%%%%%%
\textbf{Answer:} See above.
%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%
%% YL
\item 
The reason for the loss of idiomatic meaning in (43b) but not in (43c) could be attributed to the
presence of the number 'san' in (43b). If 'san xia' is replaced with 'yi xia,' which remains a
verbal classifier, the idiomatic meaning is perserved. In this case, there appears to be no
distinction between verbal classifier and reduplication.

%%%%%%%%%%%%%%%%%%%%
\textbf{Answer:}
It is not \textit{san xia} `three times' that is special, but it is \textit{yi xia} `once' that is special.
We can replace \textit{san} `three' with any number above two,
and the distinction still exist.
But \textit{yi xia} `once' has acquired a duration reading `for a little while' that is not available to the other event quantifiers formed by \textit{xia}, which only have the `for X times' interpretation (\citealt[77]{Deng2013}, \citealt[16]{Zhang2000}).
We think \textit{liang xia} `twice' is following this tendency, too.
In this case, it is easy to interpret \textit{yi xia} and \textit{liang xia} not as referring to the actual number of action taking place, 
but as duration adverbials as a whole,
thus differing them from ``actual'' verbal classifier phrases with other numerals.
%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%
%% Stefan
\item
It would enhance reader comprehension if the authors could provide a brief illustration of symbols
like HOOK, LTOP, IND, ARG, etc. This will aid readers in better grasping the authors' subsequent
proposals in Section 4.

@@

\textbf{Answer:} PHON is not missing. The constraints regarding PHON on the mother and the daughter are coming from
another constraint. A constraint that is a subtype in the hierarchy. The type
perfective-reduplication-lr in (51), which says that the PHON value of the daughter \ibox{1} appears
twice in the PHON value of the mother with some other material (\etag) between the two occurrences of \ibox{1}. 
%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%

\end{enumerate}

\section{Reviewer 3}

%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%
%% YL
\begin{enumerate}
\item The following paragraph looks terse to me. The author(s) want to provide more explanation about the four tests. In addition, the footnote 6 might be better to move into the body.
Duanmu (1998) and Schäfer (2009) proposed the following four tests to distinguish words from phrases
in Mandarin Chinese: semantic compositionality, phrasal extension, phrasal substitution and
conjunction reduction.

@@

In Page 14, the draft makes use of a new terminology such as “word-like”. Of course, I can understand the meaning within the context. However, I think the author(s) might be better to use a more academic and formal terminology.

%%%%%%%%%%%%%%%%%%%%%%
\textbf{Answer:} reformulate as ``behaves more similar to a word''.

%%%%%%%%%%%%%%%%%%%%%%
\item
Section 3 (Previous Analysis) appears in Page 17. I think it would be a little bit late. The author(s) may have a plan to restructure Sections 2 and 3 again.

%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%
%% YL
\textbf{Answer:} Since the discussion on the pros and cons of previous analyses relies heavily on understanding the syntactic and semantic constraints of reduplication, we believe that it is necessary to discuss the phenomenon thoroughly before discussing previous analyses.

%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%
%% Stefan
\item
In Page 26, the draft introduces a new notion (i.e., an empty rectangle) into the AVMs. Is it what the author(s) invent only for modeling the verbal reduplication in this drat? If so, the author(s) want to account more for how it works in AVMs. Otherwise, the author(s) might be better to refer to the previous analysis about the notion.

### 2024-07-13 replies-reviews.tex

4) Conjunction reduction. This criterion can only be applied to set apart coordinated phrases from coordinate compound words with a head in common (e.g. ‘K huiché e ¥4 giché in (33) share the head  ché ‘vehicle’). But the examples provided by the author(s) to argue against conjunction reduction with reduplicated verbs are completely different: the verbs do not have the head in common (exx. 34). I believe that this is not a reasonable test to argue for the wordhood of reduplicated verbs.

In summary, the tests used to support the morphological status of reduplication appear
unconvincing. 
\end{displayquote}

%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%
\textbf{Answer:}
Based on the suggestions by the reviewers and further literature research, this section is drastically revised.
The tests of semantic compositionality and conjunction reduction are deemed unreliable.
\citet[37--38]{Dai1992}, \citeyear[120--122]{Dai1998} explains the problems of conjunction reduction (he calls it ``coordination'').
That leaves us with phrasal extension (or ``modification'' according to \citealt[32]{Dai1992}, \citeyear[117]{Dai1998}) 
and phrasal substitution (or ``expansion'' according to \citealt[33]{Dai1992}, \citeyear[117--120]{Dai1998}).
These tests requires further clarifications.

First, the modification test suggests that subparts of a word cannot be modified at a phrasal level.
This is possible for a VP (\ref{ex:modVP}), as the NP inside of the VP can be modified by e.g. an AP.
\ea\label{ex:modVP} %开红色的门
\gll \objex{kai1} \objex{hong2se4de} \objex{men2}\\
open  red door\\
\glt `open the red door'
\z
In contrast, the individual verbs in reduplication cannot be modified by an e.g. AdvP.
(\ref{ex:modVV}) is ungrammatical whether the AdvP is interpreted to modify the first or the second verb.
\ea[*]{\label{ex:modVV} %看偷偷地看
\gll \objex{kan4} \objex{tou1tou1de} \objex{kan4}\\
look secretly look\\
}
\z

@@

\itdopt{Stmü: Fix examples and referecnes to them.}

Second, the expansion test suggests that a phrasal dependent (either a modifier or an argument) cannot be inserted into a word.
This is possible for a verbal classifier phrase (\ref{ex:inVCP}), as the object can occur after or in-between.
\ea\label{ex:inVCP}%开两次门
%开门两次
\ea \gll \objex{kai1} \objex{men2} \objex{san1} \objex{ci4}\\
open door three time\\
\glt `open the door three times'

\ex  \gll \objex{kai1}  \objex{san1} \objex{ci4} \objex{men2}\\
open three time door\\
\glt `open the door three times'
\z\z
For reduplication, this is also not possible (\ref{ex:inVV}), as the object cannot be inserted between the two verbs.
\ea\label{ex:inVV}
\ea[]{\gll \obj{kai1}-(\obj{le})-\obj{kai1} \objex{men2}\\
open-\textsc{pfv}-open door\\
\glt `open the door for a little while'}

\ex[*]{%开(了)门(了)开
\gll \obj{kai1}-(\obj{le})-\obj{men2}-\obj{kai1}\\
open-\textsc{pfv}-door-open\\
}
\z\z
% If we analyze reduplication as a phrasal operation, we would expect the structure of
% [VP [VP [V-le V]] O]
% Since both phrases are VP, there should be nothing against the following strucutre:
% [VP [VP [V-le O]] V]
% However, this is not possible.

Regarding the position of \obj{le}, there are counter-examples that show V-\obj{le-gei3} (\ref{ex:Vgei}) as well as \obj{guan1-le-xin1} `close-\textsc{pfv}-heart, care for' (\ref{ex:guanxin}) are possible.
\ea\label{ex:Vgei}%还有许多女子，将自己的相片，亲笔签字在上面，寄了给他。(CCL)
\gll \ldots\, \objex{xu3duo1} \objex{nv2zi3}, \objex{jiang1} \objex{zi4ji3de} \objex{xiang4pian1} \ldots\, \objex{ji4-le-gei3} \objex{ta1}.\\
{} many women take own photo {} send-\textsc{pfv}-give he\\\jambox{(CCL)}
\glt `Many women \ldots\, sent him photos of themselves.'
\z

\ea\label{ex:guanxin}%许多同志看戏以后，自动的对病员关了心。大家情绪很高... (CCL)
\gll \objex{xu3duo1} \objex{tong2zhi4} \ldots\, \objex{zi4dong4de} \objex{dui4} \objex{bing4yuan2} \objex{guan1-le-xin1}.\\
many comrade {} voluntarily to patient close-\textsc{pfv}-heart\\
\glt `Many comrades \ldots\, voluntarily cared for the patients.'
\z

In any case, since reduplication is not compounding (\citealt[149--150]{Sui2018}; \citealt{GaoEtAl2021} provides empirical evidence.), 
and the patterns discussed here constitute a different process than the AABB pattern 
(see the discussion on \citealt{Xie2020} in our paper, also \citealt[Sec. 4.3]{Deng2013}, \citealt[Sec. 2]{SuiHu2016}, \citealt{Sui2018} and \citealt{Wang2023}),
it is not surprising that \textit{le} occurs at a different position.

@@

%%%%%%%%%%%%%%%%%%
\textbf{Answer:}
Since the reviewer deemed it irrelevant, the section concerning \citet{Ghomeshietal2004} is removed.

%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%
%% YL
\item Pp. 26, lines 24-25: ``The output reduplicates the phonology (phon) of the input verb with the possibility to have further phonological material in between. [] indicates an underspecified list which could be empty or not''. However, it is not entirely clear what prevents phonological material other than yi and le to appear in between the reduplicated elements. This aspect seems to be somewhat arbitrary, and it is not evident why certain elements are permissible while others are not.

%%%%%%%%%%%%%%%%%%%%
\textbf{Answer:}
\obj{le} `\textsc{pfv}' marks the perfective aspect.
The reason for \obj{le} `\textsc{pfv}' being the only aspect marker compatible with reduplication is explained in the Semantics Section.

As for \obj{yi} `one', its use stems from the historical development of delimitative verbal reduplication but is synchronically opac.
\citet[13--15]{Zhang2000} shows that delimitative verbal reduplication originates from the ``V + numeral + verbal classifier'' phrase,
where the verbal classifier is borrowed from a verb of the same form, as shown in (\ref{ex:hist1}).
\ea\label{ex:hist1} 
%明又喝,岐亦喝,明连喝两喝,岐便礼拜。(《宋代卷·虚堂和尚语录》3 87 页) as cited in \citet[12]{Zhang2000}
\gll \objex{ming2} \objex{you4} \objex{he4}, \objex{qi2} \objex{yi4} \objex{he4}, \objex{ming2} \objex{liang2} \objex{he4} \objex{liang3} \objex{he4}, \objex{qi2} \objex{bian4} \objex{li3bai4}\footnotemark\\
Ming agian call Qi also call Ming in.succession call two call Qi thus bow\\
\glt `Ming called again. Qi called too. Ming called twice. Qi thus bowed.'
\z
\footnotetext{《宋代卷·虚堂和尚语录》3 87 页) as cited in \citet[12]{Zhang2000}}
Here the numeral refers to the actual number of the action taking place 
and can be any number.
This evolves into the structure of V-\obj{yi}-V (or A-\obj{yi}-A), which does not express the actual number of the action anymore,
but simply conveys that the action happens in a short period of time or for only few times (\ref{ex:hist2}).
\ea\label{ex:hist2}
且歇一歇了,去坐地。(《宋代卷·张协状元》5 19 页) as cited in \citet[13]{Zhang2000}
\z
In this case, \obj{yi1} `one' cannot be replaced by other numerals.
Since V-\obj{yi}-V does not express the actual number of the action anymore, 
it became possible to delete the \obj{yi1} `one',
hence the use of the VV (or AA) form, too.
